%!TEX program = pdflatex
\documentclass[UTF8]{article}

\usepackage[UTF8]{ctex}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}

\title{Homework 10.26}
\author{SA18225036 陈旻}

\begin{document}
\maketitle
\section{Question 33}
\paragraph{Question}
Fill in the rows of Pascal’s triangle corresponding to $n = 9$ and 10.
\paragraph{Answer}
\begin{center}
    1 9 36 84 126 126 84 36 9 1 \\
    1 10 45 120 210 252 210 120 45 10 1 \\
\end{center}
\section{Question 34}
\paragraph{Question}
Prove, that for every integer $n > 1$,
$$\begin{pmatrix} n \\ 1 \end{pmatrix} 
- 2\begin{pmatrix} n \\ 2 \end{pmatrix}
+ 3\begin{pmatrix} n \\ 2 \end{pmatrix}
+ \cdots +
\left( -1\right)^{n-1}n\begin{pmatrix} n \\ n \end{pmatrix}
 = 0
$$
\paragraph{Answer}
$$ \left(1-x\right)^n = \sum_{k=0}^{n}\begin{pmatrix} n \\ k \end{pmatrix} \left(-1\right)^{k} x^{k}$$
$$ -n\left(1-x\right)^{n-1} = \sum_{k=0}^{n}\begin{pmatrix} n \\ k \end{pmatrix} \left(-1\right)^{k} kx^{k-1}$$
\begin{center}
    Set $x = 1$
\end{center}
$$ 0 = \sum_{k=0}^{n}\begin{pmatrix} n \\ k \end{pmatrix} \left(-1\right)^{k} k$$

\section{Question 35}
\paragraph{Question}
Every day a student walks from her home to school, which is located 10 blocks east and 14 blocks north from home. She always takes a shortest walk of 24 blocks.
\begin{enumerate}[(a)]
    \item How many different walks are possible?
    \item Suppose that 4 blocks east and 5 blocks north of her home lives her best
    friend, whom she meets each day on her way to school. Now how many
    different walks are possible?
    \item Suppose, in addition, that 3 blocks east and 6 blocks north of her friend’s
    house there is a park where the two girls stop each day to rest and play. Now
    how many different walks are there?
    \item Supposing at a park to rest and play, the two students often get to school late.
    To avoid the temptation of the park, our two students decide never to pass
    the intersection where the park is. Now how many different walks are there?
\end{enumerate}

\paragraph{Answer}
\begin{enumerate}[(a)]
\item $ \begin{pmatrix} 24 \\ 10 \end{pmatrix} $
\item $ \begin{pmatrix} 9 \\ 4 \end{pmatrix} \begin{pmatrix} 15 \\ 6 \end{pmatrix}$
\item $ \begin{pmatrix} 9 \\ 4 \end{pmatrix} \begin{pmatrix} 9 \\ 3 \end{pmatrix} \begin{pmatrix} 6 \\ 3 \end{pmatrix}$
\item $ \begin{pmatrix} 9 \\ 4 \end{pmatrix} \begin{pmatrix} 15 \\ 6 \end{pmatrix} - \begin{pmatrix} 9 \\ 4 \end{pmatrix} \begin{pmatrix} 9 \\ 3 \end{pmatrix} \begin{pmatrix} 6 \\ 3 \end{pmatrix}$
\end{enumerate}
\section{Question 37}
\paragraph{Question}
Find the number of integers between 1 and 10,000 inclusive that are not divisible by 4, 5, or 6.
\paragraph{Answer}
Set A which divisible by 4. $10^{4} = 2500 * 4 $ so $\vert A \vert = 2500$ \\
Set B which divisible by 5. $10^{4} = 2000 * 5 $,so $\vert B \vert = 2000$ \\
Set C which divisible by 6. $10^{4} = 1666 * 6 + 4$,so $\vert C \vert = 2500$ \\
$10^{4} = 500 * 20$,so $\vert A \cap B \vert = 500$ \\
$10^{4} = 333 * 30 + 10$,so $\vert B \cap C \vert = 333$ \\
$10^{4} = 833 * 12 + 4$,so $\vert A \cap C \vert = 833$ \\
$10^{4} = 166 * 60 + 40$,so $\vert A \cap B \cap C \vert = 166$ \\
$\vert \bar{A} \cap \bar{B} \cap \bar{C}\vert = 10^{4} - 2500 - 2000 - 1666 + 500 + 333 + 833 - 166 = 5334$
\section{Question 38}
\paragraph{Question}
Find the number of integers between 1 and 10,000 that are neither perfect squares nor perfect cubes.
\paragraph{Answer}
Set A which perfect squares. $10^{4} = 100^{2} $ so $\vert A \vert = 100$ \\
Set B which perfect cubes. $21^{3} = 9261$ and $22^{3} = 10648$ ,so $\vert B \vert = 21$ \\
$4^{6} = 4096$ and $5^{6} = 15625$,so $\vert A \cap B \vert = 4$ \\
$\vert \bar{A} \cap \bar{B} = 10^{4} - 100 -21 +4 = 9883$
\end{document}